Object-Oriented Internet - Azure Interoperability

### 2020-11-22 Latex/Manuscript.tex
Work out Markdown\60.GatewayImplementation.md #35
- working copy
Work out Markdown\60.GatewayImplementation.md #35
- refine the text and add final content.
-

Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical Systems (CPS) designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end requires decisions addressing the selection of the services supporting web user interface capable to expose process data. In this context, the service is any autonomous (with own identity) software component or module that is interfacing with selected (CPS) for data collection, analysis, and also remote control. Microsoft Azure is a cloud-based product. It offers a vast variety of services. This virtual environment handles an unlimited number of users and devices organized using a solution concept. The solution aggregates users, devices, services, and required additional resources scoping on a selected scenario. The solution serves as a context that provides a scope to the identifiers (the names of devices, users, process data entities, etc) inside it. Solutions are used to organize deployment entities into logical groups and prevent identity collisions.

@@

From the cloud side, it is proposed to employ the \textit{IoT\ Hub}
service to handle the network traffic targeting the cyber-physical
system. This service offers profiles of the AMQP, MQTT, HTTPS protocol
stacks. In any case, process data (telemetry) is transparently
transferred back-and-forth to the upper layer \textit{IoT\ Central}
service. Hence, the payload formatting is determined by the DCM
associated with the \textit{IoT\ Central} solution. All the mentioned
protocols are standard ones. Consequently, it is possible to apply any
available implementation compliant with an appropriate specification to
achieve connectivity. In this case, all parameters required to establish
connectivity and security-context is up to the external software
responsibility. Alternatively, the API offered by the dedicated
libraries may be used. Using this API the configuration process can be
reduced significantly. Using these libraries, the selection of the
communication protocol has an indirect impact on the interoperability
features, including performance. The connectivity with
\textit{IoT\ Hub}, for example, can be obtained using:

\begin{itemize}
      \item \textit{Microsoft.Azure.Devices} - Service SDK for Azure IoT Devices
      \item \textit{Microsoft.Azure.Devices.Client}- Device SDK for Azure \textit{IoT\ Hub}
      \item \textit{Microsoft.Azure.Devices.Shared} - Common code for Azure IoT Device and Service SDK
      \item \textit{Microsoft.Azure.Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
      \item \textit{Microsoft.Azure.Devices.Provisioning.Transport.Amqp} - Provisioning Device Client AMQP Transport for Azure IoT Devices
      \item \textit{Microsoft.Azure.Devices.Provisioning.Transport.Http} - Provisioning Device Client Http Transport for Azure IoT Devices
      \item \textit{Microsoft.Azure.Devices.Provisioning.Transport.Mqtt} - Provisioning Device Client MQTT Transport for Azure IoT Devices
\end{itemize}

@@

\subsection{Preface}

@@

The \textit{PartBindingFactory} implements the \textit{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network. The received data is driven to \textit{CommunicationContext} for further processing and pushing to cloud-based services to the Azure services using configured out-of-band protocol.

\textit{IEncodingFactory} and \textit{IMessageHandlerFactory} interfaces (Fig. \ref*{figure2.UADataApplicationArchitecture} have been implemented in independent libraries and ae not considered for any modifications to deploy \textit{Embedded Gateway} functionality. The current implementation of the mentioned interfaces is localized at run time as services using an instance of the \textit{IServiceLocator}. In this example, it is assumed that \textit{IServiceLocator} \footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} } is implemented to resolve references to any external services.

\hyphenation{IDTOPro-vider}

The Azure interconnection is realized using the \textit{CommunicationContext}. It establish the out-of-band communication stack and implements message encoder. The encoded data is gathered from the \textit{PartBindingFactory} using the \textit{IDTOProvider} that defines a contract used to pull data transfer object created from a selected subscription.

\subsection{Out-of-band Protocol Selection}

\todo{Add any information about available reusable deliverables related to this work.}

The Azure supports the HTTP, AMQP, MQTT (Sec. \ref*{azure-main-technology-features}). On other hand the PubSub supports Ethernet, UDP, AMQP, MQTT {Sect. \ref*{ooi-main-technology-features}}. If the Ethernet or UDP has been selected to build interconnection based on PubSub direc interoperability between the Azure and PubSub is impossible because the mentioned protocols are not offered as the native communication services.

\subsection{Data Mapping}

For both the schema is different Data Transfer Object encoding

The Azure uses JSON based Data Transfer Object encoding and schema defined based on the solution metadata. The pubsub uses json and binary Data Transfer Object encoding. If JSON is used possibility to establish semantic context depends on the Azure metadata definition. In case PubSub uses binary encoding establishing interconnection is impossible.

\subsection{Security}

Azure and PubSub uses different security mechanism so establishing directly security context is impossible at all

\subsection{Deployment phases}

\begin{itemize}
      \item Design
      \item Gateway and devices registration
      \item Authentication
      \item Device/Service association
      \item Device/Application association
      \item Establishing session
            \begin{itemize}
                  \item Device/Device Template (Device Capability Model) association - establishing a semantic-context
                  \item Security management - establishing security-context
            \end{itemize}
      \item Interconnection - exchange of data
      \item Communication maintenance
\end{itemize}

@@

>>>>

Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} Cyber-Physical Systems (CPS) designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end requires decisions addressing the selection of the services supporting web user interface capable to expose process data. In this context, the service is any autonomous (with own identity) software component or module that is interfacing with selected (CPS) for data collection, analysis, and also remote control. Microsoft Azure is a cloud-based product. It offers a vast variety of services. This virtual environment handles an unlimited number of users and devices organized using a solution container concept. The solution aggregates users, devices, services, and required additional resources scoping on a selected scenario. It also serves as a context that provides a scope to the identifiers (the names of devices, users, process data entities, etc) inside it. Solutions are used to organize deployment entities into logical groups and prevent identity collisions.

@@

From the cloud side, it is proposed to employ the \textit{IoT\ Hub}
service to handle the network traffic targeting the cyber-physical
system. This service offers profiles of the AMQP, MQTT, HTTPS protocol
stacks. In any case, process data (telemetry) is transparently
transferred back-and-forth to the upper layer \textit{IoT\ Central}
service. Hence, the payload formatting is determined by the DCM
associated with the \textit{IoT\ Central} solution.

@@

\subsection{Gateway Implementation Architecture}\label{subsection.GatewayImplementationArchitecture}

@@

The \textit{PartBindingFactory} implements the \textit{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network. The received data is driven to \textit{CommunicationContext} for further encoding and finally pushing it to the Azure services using configured out-of-band protocol.

\textit{IEncodingFactory} and \textit{IMessageHandlerFactory} interfaces (Fig. \ref*{figure2.UADataApplicationArchitecture} have been implemented in independent libraries and ae not considered for any modifications to deploy \textit{Embedded Gateway} functionality. The current implementation of the mentioned interfaces is localized at run time as services using an instance of the \textit{IServiceLocator}. In this example, it is assumed that \textit{IServiceLocator} \footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} } is implemented to resolve references to any external services. Both interfaces are used to manage interconnection of the node with the \textit{Cyber-physical Network}.

The Azure interconnection is realized using the \textit{CommunicationContext}. It implements message encoder and establishes the out-of-band communication stack.

The recovered data from the \textit{Message} is obtained from the \textit{PartBindingFactory} using the \textit{IDTOProvider} that defines a contract used to pull the Data Transfer Object (DTO) created from a selected subscription by the \textit{PartBindingFactory}. The transfer process requires data conversion from source to destination encoding, i.e. replacing bitstreams used by the CPS by equivalent ones for the cloud-based services. The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the CPS. The Azure uses JSON based Data Transfer Object encoding and schema defined based on the solution metadata. The pubsub uses json and binary Data Transfer Object encoding. In any case the data recovered from the Message pulled from a subscription is stored locally using the object model based on standard .NET types. \textit{PartBindingFactory} maps selected object graph onto the JSON message required by the cloud services.

The encoded JSON messages must be transferred over the network to Azure using selected protocol stock. The Azure supports the HTTP, AMQP, MQTT (Sec. \ref*{azure-main-technology-features}). All the mentioned protocols are standard ones. Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity. In this case, all parameters required to establish connectivity and security-context is up to the external software responsibility. Alternatively, the API offered by the dedicated libraries may be used. Using this API the configuration process may be reduced significantly. Using these libraries, the selection of the communication protocol has an indirect impact on the interoperability features, including performance. In the proposed gateway implementation the Azure interconnection has been obtained using the following \textit{Microsoft.Azure} libraries:

\begin{itemize}
      \item \textit{Devices} - Service SDK for Azure IoT Devices
      \item \textit{Devices.Client} - Device SDK for Azure \textit{IoT\ Hub}
      \item \textit{Devices.Shared} - Common code for Azure IoT Device and Service SDK
      \item \textit{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
      \item \textit{Devices.Provisioning.Transport.Amqp} - Provisioning Device Client AMQP Transport for Azure IoT Devices
      \item \textit{Devices.Provisioning.Transport.Http} - Provisioning Device Client HTTP Transport for Azure IoT Devices
      \item \textit{Devices.Provisioning.Transport.Mqtt} - Provisioning Device Client MQTT Transport for Azure IoT Devices
\end{itemize}

Azure and PubSub uses different security mechanism so in the proposed solution establishing security context is realized independently. The \textit{CommunicationContext} is responsible to establish this context as an embedded negotiation phase closely coupled with the establishing interconnection. In this interconnection the following steps are distinguished:

\begin{itemize}
      \item Gateway and devices registration
      \item Authentication
      \item Device/Service association
      \item Device/Application association
      \item Establishing session
            \begin{itemize}
                  \item Device/Device Template (Device Capability Model) association - establishing a semantic-context
                  \item Security management - establishing security-context
            \end{itemize}
      \item Interconnection - exchange of data
      \item Communication maintenance
\end{itemize}

@@

The Azure supports the HTTP, AMQP, MQTT (Sec. \ref*{azure-main-technology-features}). On the other hand the PubSub supports Ethernet, UDP, AMQP, MQTT {Sect. \ref*{ooi-main-technology-features}}. Sets of supported protocol are not overlapping. If the Ethernet or UDP has been selected to build PubSub interconnection the direc interoperability between the Azure and PubSub is impossible because the mentioned protocols are not offered as the native communication services. In this case only indirect interconnection is available.
